The Direction of Search for a Forest Based Bioeconomy

### 2023-09-21 docs/reports/paper/paper1.qmd
update papersize to a4

csl: https://zotero.org/styles/apa?source=1
bibliography: [../../swinno-shades-green.bib]
link-citations: true
link-bibliography: true
colorlinks: true
number-sections: true
format:
    wordcount-pdf: default
execute:
    include: true
    echo: false
    warning: false
---

@@

## Discussion

# References

>>>>

csl: https://zotero.org/styles/apa?source=1
bibliography: [../../swinno-shades-green.bib]
link-citations: true
link-bibliography: true
colorlinks: true
number-sections: true
format:
    wordcount-pdf: 
        papersize: A4
execute:
    include: true
    echo: false
    warning: false
---

@@

# Discussion

{{< pagebreak >}}

# References {.unnumbered}
